Looking for a Signal in the Noise: Revisiting Obesity and the microbiome

### 2016-03-25 Sze_ObesityMicrobiomeMeta_PeerJ_2016.Rmd
manuscript update writing

```{r Figure_2, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r Figure_4, echo=FALSE}
par(mfrow=c(1,2))
funnel(res, main="A")
funnel(res2, main="B")
```

>>>>

```{r Figure_2, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, fig.path="results/figures/"}

@@

```{r Figure_4, echo=FALSE, fig.path="results/figures/"}
par(mfrow=c(1,2))
funnel(res, main="A")
funnel(res2, main="B")
```
